Cognate Priming

### 2023-07-17 docs/index.qmd
Make dashboard in Quarto

m |> 
	ggplot(aes(timebin,
			   Estimate,
			   colour = trial_type,
			   fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, 
			   size = 1,
			   colour = "grey") +
	geom_ribbon(aes(ymin = Q2.5,
					ymax = Q97.5),
				colour = NA,
				alpha = 1/3) +
	geom_line(linewidth = 3/4) +
	stat_summary(fun = median, geom = "line", size = 1) +
	geom_point(data = ptlt_means,
			   aes(y = plogis(.logit))) +
	labs(x = "Time (ms)",
		 y = "Proportion of target looking time",
		 colour = "Prime",
		 fill = "Prime",
		 shape = "Prime",
		 linetype = "Trial type") +
	scale_x_continuous(labels = \(x) format(250 + x*100, big.mark = ",")) +
	scale_y_continuous(limits = c(0, 1)) +
	theme(legend.position = "top",
		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
		  panel.grid.minor = element_blank(),
		  legend.title = element_blank())
```

>>>>

m |> 
	ggplot(aes(timebin,
			   Estimate,
			   colour = trial_type,
			   fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, 
			   size = 1,
			   colour = "grey") +
	# geom_ribbon(aes(ymin = Q2.5,
	# 				ymax = Q97.5),
	# 			colour = NA,
	# 			alpha = 1/3) +
	# geom_line(linewidth = 3/4) +
	# stat_summary(fun = median, geom = "line", size = 1) +
	geom_point(data = ptlt_means,
			   aes(y = plogis(.logit))) +
	labs(x = "Time (ms)",
		 y = "Proportion of target looking time",
		 colour = "Prime",
		 fill = "Prime",
		 shape = "Prime",
		 linetype = "Trial type") +
	scale_x_continuous(labels = \(x) format(250 + x*100, big.mark = ",")) +
	scale_y_continuous(limits = c(0, 1)) +
	theme(legend.position = "top",
		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
		  panel.grid.minor = element_blank(),
		  legend.title = element_blank())
```
